Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-08-08 paper/letter.tex
dynamical mass multiphase

Both the rotation and the multiphase model constrain the typical
velocity of the HI gas, with and additional constrain on the typical
size for the emission region, $D$, on could estimate a dynamical mass with

\begin{equation}
M_{\rm dyn} = \frac{V^{2}D}{G} = 2.16\times10^{5}
\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
\end{equation}

The multiphase model also sets a typical size for the region where the
clumps are confined.
In the rotation model the size of that region can be infered from the
constraint on the total HI mass.

From the optical depth of $10^7$ and the non-detection in the HI line,
we have an upper limit for the size where the Lya emission comes of
$D<0.34$kpc.

>>>>

Both the rotation and the multiphase model constrain the typical
velocity $v$ of the HI gas, with and additional constrain on the typical
size for the emission region $r$ on could estimate a dynamical mass with

\begin{equation}
M_{\rm dyn} = \frac{v^{2}r}{G} = 1.16\times10^{9}
\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
\end{equation}

From the multiphase model we obtained $v=71_{-25}^{+16}$ \kms
and $r=5$ kpc. 
This corresponds to a dynamical mass of $M_{\rm
  dyn}=5.9^{+3.1}_{-3.4}\times 10^{9}$ $M_{\odot}$ which is at least
$20$ times the HI mass estimated from observations.

In the rotation model the size of that region can be infered from the
constraint on the total HI mass.
From the optical depth of $10^7$ and the non-detection in the HI line,
we have an upper limit for the size where the Lya emission comes of
$D<0.34$kpc.
